Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex

### 2019-04-15 Manuscript.Rmd
Addressed most of Sean's comments on Intro, methods, and Results

---
title: 'Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex'
author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
output:
  pdf_document: 
    keep_tex: true
  word_document: 
    reference_docx: Style_reference_draft.docx
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

@@

  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018]. One such function is subjective valuation during economic decision making [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011]. Both mPFC and PCC (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued. These regions are also implicated in a set of functions associated with the default-mode network (DMN). DMN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Fox2005; @Yeo2011].

  Coordinate-based meta-analyses of the fMRI literature have demonstrated that valuation and DMN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017]. The two sets of effects diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DMN. Within PCC and adjacent precuneus, a more posterior subregion appears DMN-specific, whereas a more anterior subregion is implicated in both effects. One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within the distributed brain systems that subserve valuation and DMN effects. The potential existence of common nodes has primpted theorizing about posible cognitive-level overlap between valuation and DMN-related processes. For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Northoff2012; @Clithero2014; @Acikalin2017; @Reddan2018].

  However, to draw firm conclusions about functional overlap will require a better understanding of individual-level heterogeneity in topographic patterns of brain activity. A key limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Woo2014; @Michalka2015; @Wang2015], potentially exaggerating the degree of overlap across domains. This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Laumann2015; @Gordon2017; @Gratton2018b; @Tobyne2018]. Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DMN through tailored analyses of seed-based functional connectivity [@Braga2017; @Braga2019]. It is therefore possible that the diffuse overlap of DMN and valuation effects can be attributed to a lack of spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level. An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DMN effects within mPFC and PCC.

  A useful way to characterize individual-specific brain organization is to examine patterns of resting-state functional connectivity (rsFC; i.e. time-series correlations between pairs of locations in the brain). Connectome-based analyses of rsFC have been fruitful in characterizing individualized functional topologies that correspond well to task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017; @Smith2009]. A popular way to analyze these connectomes is to rely on graph theoretic methods, which are properly equiped to understand brain network dynamics [@Bassett2018a]. In the context of network analysis, community detection algorithms have been successfully used to subdivide brain networks into multiple distinct communities [@Garcia2017]. Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016]. In attempting to refine the DMN topography at the individual level, we focus on dividing mPFC and PCC into communities encapsulating what belongs and does not belong to DMN. Spectral partitioning (SP) is an efficient community detection algorithm that deterministically forces such bisections [@Fiedler1975; @Belkin2003]. For a network composed of pairwise correlations among its nodes, SP partitions the network by binarizing the eigenvector linked to the second-to-lowest eigenvalue of the adjusted (Laplacian) correlation matrix according to its sign (i.e. positive or negative number). SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018], and was recently shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019]. This method can therefore capture a refined group of brain regions that more cohesively share activation patterns during rest.

  In this study, we aimed to subdivide regions commonly attributed to both DMN and subjective valuation into individual-specific DMN and non-DMN communities, quantifying the degree of topographical heterogeneity present in this network within and across individuals. We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks. First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DMN and limbic networks along the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of DMN and SV literatures identified a parcel in PCC that was DMN-specific at the aggregate level. We then derived an rsFC network of all the surface vertices within the search space for each of `r nSubj` individual resting-state fMRI data sets from the Human Connectome Project (HCP)[@VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographical extent of each community. The resulting communities varied topographically across subjects, while also appearing to follow common organizational principles. A combination of sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. Lastly, we provide evidence that the resulting communities resembled an organizational scheme recently observed in a handful of subjects [@Braga2017]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.

@@

For all analyses, we defined our search space based on the 17-network parcellation proposed by Yeo et al. [-@Yeo2011]. First, we selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial wall. Next, we overlayed those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions. This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1). The search space was naturally divided into two spatially discontiguous clusters that covered PCC and mPFC, facilitating the study of each general region separately.

@@

We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DMN effects. For subjective valuation, we gathered peak brain coordinates of activity from 200 studies that were associated with positive effects for current or prospective rewards [@Bartra2013]. For DMN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009]. These coordinates represent the areas that exceeded the statistical significance threshold in each original study. For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009]. The indicator map for each study was then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/). Any sphere sections that overlapped with the cortex (no lower limit restrictions) were mapped to the corresponding parcel, and we tallied how many studies had positive indicator values in each parcel. Two studies from the subjective valuation corpus were removed because they did not contain cortical voxels, leaving a final number of 198 studies.

With these lists, we tested for parcels that were significantly more strongly associated with one domain than the other. We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains. This gave us a null distribution of 5000 maximum chi-squared values. The 95th percentile of this distribution served as an FWE-corrected significance threshold to evaluate unpermuted chi-squared values.

@@

``` {r fMRI data descriptives} 
# load file with the n of TRs and density data
corrCounts <- read.csv('corrCounts.csv')
```
Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state runs (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised up to 1200 time points(14 min 33 s) for a total of up to 4800 time points (median = `r median(corrCounts$nTR)`, minimum = `r min(corrCounts$nTR)`). Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other. Only subjects with both left-right and right-left phase encoding were included (i.e. subjects with four rsfMRI sessions). In addition, only datasets with either low motion levels (under 1.5 mm) or under 0.5 mm mean framewise displacement (FD) were used. See [@VanEssen2012] for more details about the data acquisition protocol.

Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, temporal denoising based on independent components (FIX, [@Griffanti2014; @Salimi-Khorshidi2014]), high-pass filtering (0.0005 Hz threshold), and MNI152-based normalization. Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017]. Steps included linear interpolation across timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising and high-motion censoring by deletion, as well as mean greyordinate signal regression [@Burgess2016]. Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses. Finally, data acquired on the same day (i.e. left-right and right-left phase encoding session) were temporally demeaned. Each subject's brain was comprised of 32k standard HCP greyordinates per hemisphere (combined in a CIFTI file). We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.

@@

All network analyses were performed using the igraph package [@G.2006] in R 3.4.1 [@RTeam2018]. To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, in which the nodes were surface vertices and the edges were the correlations among them. Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify strong correlations. The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values). The proportion of remaining edges (i.e. network density) was high for all individuals (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`), which were mostly composed of positive correlations (positive: mean = `r mPos`, sd = `r sdPos`; negative: mean = `r mNeg`, sd = `r sdNeg`). Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution. Values of 1 of this transformed distribution were returned to 0 in order to avoid the inclusion of these edges in the network analyses. We generated and analyzed network weight matrices at four levels: (1) for each run separately (1200 TRs each); (2) for the concatenated time series for the two runs on each day (2400 TRs total); (3) for each subject's full dataset (4800 TRs total); and (4) on each step of a sliding window analysis (see Partition Evaluation for more details).

@@

Communities (i.e. clusters) were identified using the SP algorithm [@Belkin2003; @Chung1999; @Fiedler1975]. First, each network was represented as an $n$ x $n$ network weight matrix $W$ as described above (where $n$ equals the number of vertices in the search space, 4,801). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its transformed correlation values with every other vertex), and $W$ is the network weight matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. The transformation ensures that every row sums to zero. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values and is binarized by sign [@Fiedler1975]. This method partitions the network into two similarly-sized communities, and guarantees that they share at least one edge [@Chung1999]. In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise). Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community as that which contained the DMN-specific PCC parcel identified in our meta-analysis. The high density of these networks ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].

In order to evaluate the convergent validity of the resulting partitionings across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al. [-@Clauset2004]. This method compares the strength of the connection between any two vertices to their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combinations of vertices, and selects the partitioning that maximizes the network's so-called modularity. Unlike SP, modularity can fractionate a network into more than two communities. We assumed that if the partitionings from the bounded and unbounded community detection methods showed high levels of agreement, we could gain confidence in that we were indeed fractioning the search space into an adequate number of communities. We also diagnosed our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by SP to be non-zero. This eigenvalue serves as an estimator of the optimal number of communities in a network [@Chung1999], such that a rank of two in our partitions justifies limiting the number of communities to two.

@@

In order to evaluate the stability and topographical heterogeneity of the communities within and across individuals, we chose the adjusted rand index (ARI) as a reference metric of agreement between two partitionings [@Hubert1985], which was calculated using the "mcclust" package in R [@Arno2012]. The base of the ARI is computed by the formula

@@

Where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number grouped together (separately) in one partition, but separately (together) in the other. Therefore, the ARI estimates the fraction of all possible node pairs that had the same status (connected or not) in both partitionings (with the denominator equal to $(n\times (n - 1))/2$). The resulting ratio is adjusted by comparing it to a baseline given by the expectation of a random node assignment across partitions. The index ranges from 0 to 1, where 0 denotes the value expected by chance. This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below 50%). In short, the ARI determines the chance-corrected percentage of agreement between any two partitions while being agnostic to the labeling scheme.

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP have been previously found to show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Alignment between the two algorithms would therefore give us confidence in the validity of the resulting partitionings. Next, we compared the partitionings derived from each individual's full time series across subjects, and report the mean pairwise ARI for the group. We then performed the same evaluation for PCC and mPFC separately, and examined whether there were mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects. Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all subsequent analyses on PCC and mPFC separately.

To estimate the degree of stability of these partitions per individual we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the partition derived from the whole subject's data. A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017]. We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows. To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series). Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DMN or non-DMN more than 99% of the time.

We then estimated the level of agreement between network partitions estimated using data from individual days (with 2 days per participant). If the functional organization estimated by SP is indeed individual-specific, we should see higher agreement within individual (test/re-test across days) than across individuals. We tested this idea by computing the ratio of the mean ARI within and between individuals. Ratios close to one denoted similar within-participant and across-participant alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-participant than across participants. We then extended this idea by computing the overall agreement across individual runs (4 per subject). Similar to the day-based analysis, we assessed whether run-level data showed higher agreement within-subject than between subjects.

>>>>

---
title: 'Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex'
author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
output:
  pdf_document: 
    keep_tex: true
    highlight: haddock
  word_document: 
    reference_docx: APA_style.docx #Style_reference_draft.docx 
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

2.  Graduate Program for Neuroscience, Boston University, Boston, USA

@@

  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018]. One such function is subjective valuation during economic decision making [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011]. Both mPFC and PCC (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued. These regions are also implicated in a set of functions associated with the default-mode network (DMN). DMN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Greicius2003; @Fox2005; @Yeo2011].

  Coordinate-based meta-analyses of the fMRI literature suggest that valuation and DMN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017]. The two sets of effects diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DMN. Within PCC and adjacent precuneus, a more posterior subregion appears DMN-specific, whereas a more anterior subregion is implicated in both effects. One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within the distributed brain systems that subserve valuation and DMN effects. The potential existence of common nodes has prompted theories positing overlap between valuation and DMN-related cognitive processes. For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Northoff2012; @Clithero2014; @Acikalin2017; @Reddan2018].

  However, concluding that colocalization at the group level equates to overlap in cognitive function requires a better understanding of individual-level heterogeneity in topographic patterns of brain activity. A key limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Woo2014; @Michalka2015; @Wang2015; @Tobyne2018], potentially exaggerating the degree of overlap across domains. This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Laumann2015; @Gordon2017; @Gratton2018b; @Tobyne2018]. Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DMN through tailored analyses of seed-based functional connectivity [@Braga2017; @Braga2019]. It is therefore possible that the diffuse overlap of DMN and valuation effects can be attributed to a lack of spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level. An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DMN effects within mPFC and PCC.

  A useful way to characterize individual-specific brain organization is to examine patterns of resting-state functional connectivity (rsFC; i.e. time-series correlations between pairs of locations in the brain). Connectome-based analyses of rsFC have been fruitful in characterizing individualized functional topologies that correspond well to task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017; @Smith2009]. A popular way to analyze these connectomes is to rely on graph theoretic methods, which are properly equiped to understand brain network dynamics [@Bassett2018a]. In the context of network analysis, community detection algorithms have been successfully used to subdivide brain networks into multiple distinct communities [@Garcia2017]. Such communities represent clusters of network nodes that share more connections with each other than with the rest of the network [@Fortunato2016]. In attempting to refine the DMN topography at the individual level, we focus on dividing mPFC and PCC into communities encapsulating what belongs and does not belong to DMN. Spectral partitioning (SP) is an efficient community detection algorithm that deterministically forces such bisections [@Fiedler1975; @Belkin2003]. For a network composed of pairwise correlations among its nodes, SP partitions the network by binarizing the eigenvector linked to the second-to-lowest eigenvalue of the adjusted (Laplacian) correlation matrix according to its sign (i.e. positive or negative number). SP has recently been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI (rsfMRI) data [@Tian2018], and was recently shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019]. This method can therefore capture a refined group of brain regions that more cohesively share spontaneously covarying temporal activation patterns during rest.

  In this study, we aimed to subdivide regions commonly attributed to both DMN and subjective valuation into individual-specific DMN and non-DMN communities, quantifying the degree of topographical heterogeneity present in this network within and across individuals. We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks. First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DMN and limbic networks along the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of DMN and SV literatures identified a parcel in PCC that was DMN-specific at the aggregate level. We then derived an rsFC network of all the surface vertices within the search space for each of `r nSubj` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographical extent of each community. The resulting communities varied topographically across subjects, while also appearing to follow common organizational principles. Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. Lastly, we provide evidence that the resulting automatically defined communities resembled an organizational scheme recently observed in a series of low N studies [@Braga2017; @Braga2019]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.

@@

For all analyses, we defined our search space based on the 17-network parcellation proposed by Yeo et al. [-@Yeo2011]. First, we selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial surface in HCP's 32,000 surface space (fs_LR_32k). Next, we overlaid those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions. This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1). The search space was naturally divided into two spatially discontinuous clusters that covered PCC and mPFC, facilitating the study of each general region separately.

@@

We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DMN effects. For subjective valuation, we gathered peak brain coordinates of activity from 200 studies that were associated with positive effects for current or prospective rewards [@Bartra2013]. For DMN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009]. These coordinates represent the areas that exceeded the statistical significance threshold in each original study. For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009]. The indicator map for each study was then projected to a standard cortical mesh (fsaverage, 160,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/). **TODO: The Glasser et al. (2016) parcellation was resampled to fsaverage to pair spheres to parcels from our search space**. Any sphere sections that overlapped with the cortex (no lower limit restrictions) were mapped to the corresponding parcel, and we tallied how many studies had positive indicator values in each parcel. Two studies from the subjective valuation corpus were removed because they did not contain cortical voxels, leaving a final number of 198 studies.

With these lists, we tested for parcels that were significantly more strongly associated with one domain than the other with a chi-squared test. We permuted the label of every study (i.e. DMN or valuation) 5000 times while preserving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains. This gave us a null distribution of 5000 maximum chi-squared values. The 95th percentile of this distribution served as an FWE-corrected significance threshold to evaluate unpermuted chi-squared values.

@@

``` {r fMRI data descriptives} 
# load file with the n of TRs and density data
corrCounts <- read.csv('corrCounts.csv')
```

Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (N = `r nSubj`, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state runs (repetition time = 0.720 s, echo time = 33.1 ms, flip angle = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised up to 1200 time points (14 min 33 s) for a total of up to 4800 time points (median = `r median(corrCounts$nTR)`, minimum = `r min(corrCounts$nTR)`). Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other. Only subjects with both left-right and right-left phase encoding were included (i.e. subjects with four rsfMRI sessions). In addition, only datasets with low motion levels (under 1.5 mm) and less than 5% of points over 0.5 mm framewise displacement (FD) were used. See [@VanEssen2012] for more details about the data acquisition protocol.

Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, high-pass filtering (0.0005 Hz threshold), MNI152-based normalization, surface reconstruction, and mapping of functional data to the surface (details can be found on Glasset et al., 2013). In addition, data underwent temporal denoising based on independent components [FIX; @Griffanti2014; @Salimi-Khorshidi2014]. Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017]. Steps included linear interpolation across high motion timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising via grayordinate signal regression [@Burgess2016] and censoring of high-motion timepoints by deletion. Finally, data acquired on the same day (i.e. left-right and right-left phase encoding session) were temporally demeaned. Each subject's brain was comprised of 32k standard grayordinates per hemisphere (combined in a CIFTI file). We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.

@@

All network analyses were performed using the igraph package [@G.2006; https://igraph.org/r/] in R [v. 3.4.1; @RTeam2018; https://www.r-project.org/]. To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, in which the nodes were surface vertices and the edges were the correlations among them. Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify significant connections. The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were set to 0 (all other edges retained their respective z-values). The proportion of remaining edges (i.e. network density) was high for all individuals (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`), which were mostly composed of positive correlations (positive: mean = `r mPos`, sd = `r sdPos`; negative: mean = `r mNeg`, sd = `r sdNeg`). Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution. Values of 1 of this transformed distribution were reset to 0 in order to avoid the inclusion of these edges in the network analyses. We generated and analyzed network weight matrices at four levels: (1) for each run separately (1200 TRs each); (2) for the concatenated time series for the two runs on each day (2400 TRs total); (3) for each subject's full dataset (4800 TRs total); and (4) on each step of a sliding window analysis (see Partition Evaluation for more details).

@@

Communities (i.e. clusters) were identified using the SP algorithm [@Fiedler1975; @Chung1999; @Belkin2003]. First, each network was represented as an $n$ x $n$ network weight matrix $W$ as described above (where $n$ equals the number of vertices in the search space, 4,801). This matrix was then transformed into its symmetric normalized Laplacian form

@@

Where $I$ is an identity matrix of size $n$, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its Fisher transformed correlation values with every other vertex), and $W$ is the Fisher transformed network weight matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. The transformation ensures that every row sums to zero. We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values and is binarized by sign [@Fiedler1975]. This method partitions the network into two similarly-sized communities, and guarantees that they share at least one edge [@Chung1999]. In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise). Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community as that which contained the DMN-specific PCC parcel identified in our meta-analysis. The high density of the graphs ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].

In order to evaluate the validity of the resulting partitionings across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al. [-@Clauset2004]. This method compares the strength of the connection between any two vertices to their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combinations of vertices, and selects the partitioning that maximizes the network's so-called modularity. Unlike SP, modularity can fractionate a network into more than two communities. Agreement between the partitions provided by the bounded and unbounded community detection methods would indicate confidence in the partitions.

@@

We used the adjusted Rand index (ARI) to evaluate the stability and topographical heterogeneity of the communities within and across individuals [@Hubert1985], which was calculated using the "mcclust" package in R [@Arno2012]. The base of the ARI is computed by the formula

@@

where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number of nodes grouped together (separately) in one partition, but separately (together) in the other. Therefore, the ARI estimates the fraction of all possible node pairs that had the same status (connected or not) in both partitionings (with the denominator equal to $(n\times (n - 1))/2$). The resulting ratio is adjusted by comparing it to a baseline given by the expectation of a random node assignment across partitions. The index ranges from 0 to 1, where 0 denotes the value expected by chance. This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below 50%). In short, the ARI determines the chance-corrected percentage of agreement between any two partitions while being agnostic to the labeling scheme.

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP have been previously found to show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Alignment between the two algorithms would therefore give us confidence in the validity of the resulting partitionings. Next, we compared the partitionings derived from each individual's full time series across subjects, and calculated the mean pairwise ARI for the group. We then performed the same evaluation for PCC and mPFC separately, and examined whether there were mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects. Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all subsequent analyses on PCC and mPFC separately.

To estimate the degree of stability of these partitions per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partition against the partition derived from the whole subject's data. A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017]. We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows. To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series). Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DMN or non-DMN more than 99% of the time.

We then estimated the level of agreement between network partitions estimated using data across individual scan days (with 2 days per participant). If the functional organization estimated by SP is indeed individual-specific, we should see higher agreement within individual (test/re-test across days) than across individuals. We tested this idea by computing the ratio of the mean ARI within and between individuals. Ratios close to one denoted similar within-participant and across-participant alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-participant than across participants. We then extended this idea by computing the overall agreement across individual runs (4 per subject). Similar to the day-based analysis, we assessed whether run-level data showed higher agreement within-subject than between subjects.
